The Design of Shallow State Blockchain

### 2020-06-14 abstract.tex
減少「硬碟」術語的使用
ctapc加上實驗

\begin{abstractzh}
基於區塊鏈的加密貨幣是一種點對點的交易系統，
在此去中心化的系統中，
每個節點都維護一個完整的賬本，
其中記錄了所有賬戶的全部交易資料。
這樣的系統具有不容易被竄改資料的特點，
然而此種特性會使得所需要儲存的資料只增不減，
經年累月下來，對單個節點的儲存容量要求只會越來越高，
一旦個體維護的節點逐漸不勘負荷，
將導致此區塊鏈的中心化程度逐步上升。

無狀態區塊鏈是一種針對以上問題的改進方案，
它的每一筆交易中附上了合法性證明，
使得節點不需要進入硬碟查找過往賬本資訊，
只要驗證交易內附的證明即可，
從而使節點所需儲存資訊大幅減少。

在本論文中，我們將討論以下兩點：
第一，並無必要在每一筆交易都附上證明，
只要快取部分訊息，
一筆交易的合法性很可能由最近出現過的其他交易的合法性推知。
第二，當區塊鏈發生分叉時，必須回到分叉點再產生新區塊的快取，
為此我們設計了不可變的資料結構，
使得快取能夠在各種情況下被快速計算。
最後，進行實驗來瞭解數種快取策略與資料結構在不同工作量（workload）下的表現。

@@

Cryptocurrency based on blockchain is a peer to peer trading system. In this decentralized system, each node maintain a complete ledger which records entire transaction history of all account. The system has the characteristics that it is very hard to tamper with the data. However, such characteristic only makes the data increase but do not decrease. Years after years, requirement to single node will get higher and higher. Once some entities get overwhelmed, the degree of centralization of this blockchain system will gradually rise.

Dealing with the issue, stateless blockchain is a promising approach. To be more specific, in this system, each transaction is attached with proof of validity. With this approach, there is no need for a node to access the disk to search past information of the ledger. Instead, node only verifies the proof attached to each transaction. Therefore, it will significantly reduce the space of data storage for each node.

In this paper, we will discuss the following two points.
First, it only need to cache part of information instead of attaching proof to each transaction. It is highly possible to infer the validity of a transaction from other valid transaction appearing recently. Second, when blockchain forks, it have to go back to the bifurcation point and create new cache of new blocks. To reach the purpose, we propose an immutable data structure so that cache can be rapidly computed under any situation. Finally, we conduct the experiments with different workload to understand the performance of different cache strategies and data structures.

>>>>

\begin{abstractzh}
基於區塊鏈的加密貨幣網路中，
每個節點都維護一個完整的賬本，
經年累月，賬本的儲存容量越來越高，
維護一個節點的成本也會越來越高。
無狀態區塊鏈是一種針對以上問題的改進方案，
它的每一筆交易中附上了合法性證明，
使得節點不需要進入資料儲存裝置查找過往賬本資訊，
只要驗證交易內附的證明即可，
從而使節點所需儲存的資訊量大幅減少，
然而，要付出額外的網路流量與驗證時間。

在本論文中，我們將在基於帳號的區塊鏈上討論以下兩點：
第一，
一筆交易的合法性很可能由最近出現過的其他交易的合法性推知，
只要快取帳號的訊息，
就可以省略部分交易的證明，
以此來減少網路流量與驗證時間。
第二，
快取替換有多種策略，針對 LRU 策略，
設計了基於不可變紅黑樹與不可變順序樹的兩種資料結構，
並且進行實驗比較了快取命中與快取失效的代價，
模擬現今以太坊的區塊性質，
當快取數十個區塊大小的賬戶資訊量時，
快取命中所需的查找時間仍數倍低於梅克爾 Patricia 證明驗證的時間。

@@

Cryptocurrency based on blockchain is a peer to peer trading
system. In this decentralized system,
each node maintain a complete ledger which
records entire transaction history of all account.
Years after years, requirement to single node will
get higher and higher. Dealing with the issue, stateless
blockchain is a promising approach. To be more specific,
in this system, each transaction is attached with proof
of validity. With this approach, there is no need for a node
to access the data storage device to search past information
of the ledger. Instead, node only verifies the proof attached
to each transaction. Therefore, it will significantly
reduce the space of data storage for each node.
But it will cause additional network traffic and
verification time.

In this paper, we will discuss the following two points
on the account-based.
First,
It is highly possible to infer the validity of
a transaction from other valid transaction appearing recently.
If we cache account information, we can eliminate some
proof in transactions and then reduce network traffic
and verification time.
Second,
There are so many cache replacement polices.
For LRU polices, we designed two composite data
structures which based on red-black tree and order tree.
And conduct some experiments to compare the costs of
cache hit with the penalty of cache miss.
Simulating today's Ethereum's block property,
when cache size can contain several tens of blocks' information,
the cache searching time is significantly lower than
the time to verify Merkle Patricia proofs.

### 2020-06-14 ctapc/paper.tex
ctapc加上實驗

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\begin{abstract}
Cryptocurrency based on blockchain is a peer to peer trading system.
In this decentralized system, each node maintain a complete ledger which records entire transaction history of all account.
The system has the characteristics that it is very hard to tamper with the data.
However, such characteristic only makes the data increase but do not decrease.
Years after years, requirement to single node will get higher and higher.
Once some entities get overwhelmed, the degree of centralization of this blockchain system will gradually rise

Dealing with the issue, stateless blockchain is a promising approach.
To be more specific, in this system, each transaction is attached with proof of validity.
With this approach, there is no need for a node to access the disk to search past information of the ledger.
Instead, node only verifies the proof attached to each transaction.
Therefore, it will significantly reduce the space of data storage for each node.

In this paper, we will discuss the following two points.
First, it only need to cache part of information instead of attaching proof to each transaction.
It is highly possible to infer the validity of a transaction from other valid transaction appearing recently.
Second, when blockchain forks, it have to go back to the bifurcation point and create new cache of new blocks.
To reach the purpose, we propose an immutable data structure so that cache can be rapidly computed under any situation.
Finally, we conduct the experiments with different workload to understand the performance of different cache strategies and data structures
\end{abstract}

@@

This paper proposes an imrpovement to stateless blockchain.
We let the node on stateless blockchain reach a consensus
to maintain a cache. If the payer of transaction appears
in recent transaction, it is highly possible to infer
the validity from cache. Hence, due to the omission of
proof of validity, it reduces the size of transaction and
the Internet traffic while broadcasting. However, how
to maintain cache effectively becomes a new problem.
When a new block append to the blockchain, there will be
a correspondent cache. Nevertheless, there will
also exist overlap on the blocks nearby.
Therefore, we design persisted data structure
for different cache strategies, such as the
nearest k blocks and LRU, and we conduct an
experiment to test their performance.

@@

From an abstract view, LRU is a data structure that supports two kinds of interface.
\begin{itemize}
\item get(key)
\item put(key, value)
\end{itemize}
When executing get(key), LRU will determine whether the key exists. If the key exists, it will return the value and update its using time.
When executing put(key, value), LRU will determine whether the space of LRU is full. If the space of LRU isn’t full, the key-value pair will be inserted to the space directly.  If the space of LRU is full, LRU will find out the least recently used one in the cache and abandon it, and then insert the new key-value pair to it. The using time of the new key-value pair should be the latest.
Corresponding to the situation of stateless blockchain, everytime when a new block appends to the chain, we have to compute the cache of the new block. In this time, a series of read and modify execution of accounts will turn into get and put. Key will be the address of account, and value will be the state of account. Finally, the underlying data structure of LRU will take the correspondent action.

@@

If cache size is n, the height of the order tree will be set as 1 + logn. That is to say, the number of leaves is at least two times the cache size. Fig. 3 shows that there is an order tree with size 4, and it has 8 leaf nodes.

@@

Fig. 4 shows a series of execution of order tree. In this figure, full copy happens at the time when state 7 turns into state 8. The light blue nodes in the figure mean that they are unused. Notice that we painted all unused leaves of subtree light blue.
In implementation, there is no need to allocate memory space to light blue nodes. The pointer pointing to light blue subtree is a null pointer.

@@

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
% \usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\begin{abstract}
Cryptocurrency based on blockchain is a peer to peer trading
system. In this decentralized system,
each node maintain a complete ledger which
records entire transaction history of all account.
Years after years, requirement to single node will
get higher and higher. Dealing with the issue, stateless
blockchain is a promising approach. To be more specific,
in this system, each transaction is attached with proof
of validity. With this approach, there is no need for a node
to access the data storage device to search past information
of the ledger. Instead, node only verifies the proof attached
to each transaction. Therefore, it will significantly
reduce the space of data storage for each node.
But it will cause additional network traffic and
verification time.

In this paper, we will discuss the following two points
on the account-based.
First,
It is highly possible to infer the validity of
a transaction from other valid transaction appearing recently.
If we cache account information, we can eliminate some
proof in transactions and then reduce network traffic
and verification time.
Second,
There are so many cache replacement polices.
For LRU polices, we designed two composite data
structures which based on red-black tree and order tree.
And conduct some experiments to compare the costs of
cache hit with the penalty of cache miss.
Simulating today's Ethereum's block property,
when cache size can contain several tens of blocks' information,
the cache searching time is significantly lower than
the time to verify Merkle Patricia proofs.
\end{abstract}

@@

This paper proposes an improvement to stateless blockchain.
We let the node on stateless blockchain reach a consensus
to maintain a cache. If the payer of transaction appears
in recent transaction, it is highly possible to infer
the validity from cache. Hence, due to the omission of
proof of validity, it reduces the size of transaction and
the Internet traffic while broadcasting. However, how
to maintain cache effectively becomes a new problem.
When a new block append to the blockchain, there will be
a correspondent cache. Nevertheless, there will
also exist overlap on the blocks nearby.
Therefore, we design persisted data structure
for different cache strategies, such as the
nearest k blocks and LRU, and we conduct an
experiment to test their performance.

@@

From an abstract view, LRU is a data structure that supports two kinds of interface.
\begin{itemize}
\item get(key)
\item put(key, value)
\end{itemize}
When executing get(key), LRU will determine whether the key exists. If the key exists, it will return the value and update its using time.
When executing put(key, value), LRU will determine whether the space of LRU is full. If the space of LRU isn’t full, the key-value pair will be inserted to the space directly.  If the space of LRU is full, LRU will find out the least recently used one in the cache and abandon it, and then insert the new key-value pair to it. The using time of the new key-value pair should be the latest.
Corresponding to the situation of stateless blockchain, every time when a new block appends to the chain, we have to compute the cache of the new block. In this time, a series of read and modify execution of accounts will turn into get and put. Key will be the address of account, and value will be the state of account. Finally, the underlying data structure of LRU will take the correspondent action.

@@

If cache size is n, the height of the order tree will be set as 1 + log n. That is to say, the number of leaves is at least two times the cache size. Fig. 3 shows that there is an order tree with size 4, and it has 8 leaf nodes.

@@

Fig. 4 shows a series of execution of order tree. In this figure, full copy happens at the time when state 6 turns into state 7. The light blue nodes in the figure mean that they are unused. Notice that we painted all unused leaves of subtree light blue.
In implementation, there is no need to allocate memory space to light blue nodes. The pointer pointing to light blue subtree is a null pointer.

@@

\section{experiment}
In this section, we evaluated the performances of 
persistent LRU implemented in different data 
structures under different workload.

\subsection{Experiment Environment}
All experiments were all conducted on the workstation below:

\begin{itemize}
\item CPU: AMD Ryzen 7 2700X (8 cores 16 threads, 3.6 GHz, 32K L1d cache, 64k L1i cache, 512K L2 cache、8M L3 cache)
\item memory: DDR4 64 GB
\item OS: Linux manjaro 4.19.36-1-MANJARO x86\_64
\item compiler: GCC 9.1.0
\end{itemize}

\subsection{Data Structures}

We use C++ 17 implemented three data structures:

\begin{itemize}
\item hash table + doubly-linked list, it will copy itself when creating a new version
\item persistent hash table + persistent red-black tree
\item persistent hash table + persistent order tree
\end{itemize}

Because what we want to simulate is blockchain,
all workload use block as unit.
There are many get/put instructions in a block.
To optimize this kind of workload,
the persistent data structures described above all
support transience. That means data structure doesn't 
generate a new version for every get/put instruction,
but generate an temporary ephemeral data structures and
make it immutable one after operating batch of instructions.
While eliminating lots of intermediate states,
this optimization can significantly improve performance.

We claim that, in our implementation:
Hash table is unordered\_map in C++ standard library.
For persistent hash table, we use famous C++
persistent data structures library \href{https://sinusoid.es/immer/}{immer}.
Doubly-linked list, persistent red-black tree,
persistent order tree are all implemented by ourselves.

From now on, we will refer to these three composite data structures
as doubly linked list, red-black tree, and order tree.

\subsection{performance}

\subsubsection{workload}
We use a simple model to simulate block generation,
there are n nodes in the network,
Each node will mine for the highest block
(that is, the top of the longest chain it recognizes).
Initially, The highest block of each node
is genesis block. Afterwards, there were several rounds,
In each round, each node has a certain probability
to dig out new blocks. If it is not dug,
It will go to the successor block of the
highest block dug by other nodes,
if the highest block does not have any successor block,
node will randomly go to other longest chains.
If no node has dug out any block,
the same process will be repeated.

In all workloads, it is assumed that there
are 10 nodes in the network, and the probability
of each node to dig out new block in one round is one-tenth.
The block generating process will stop after mining 1000 blocks.
Under this setting, there will be about
1.5 blocks at the same height.

From \href{https://etherscan.io/chart/gaslimit}{etherscan}, we can
know that Ethereum's gas limit is about ten million, and
it will cost 21000 gas fee per transaction.
After simple division, a block can contain about 500 transactions.
Therefore, the number of get/put instructions
for one block of our workload is set to 500.

In addition, There is another argument, get/put rate.
For normal ethereum transaction,
payment always results in state changing,
but it's not true when smart contract is involved.
Therefore, it is possible get/put instructions both appear.
If there is no additional explanation below,
the put instruction will account for 50 \% (get instruction also accounts for 50 \%).

Before starting any task, we will first fill
the entire cache, if not, when the cache size is set too large,
workload takes a long time to fill it up,
and the state when the cache is not full is not our concern,
as the blockchain is usually composed of millions of blocks,
For most of the time, the cache is full.

\subsubsection{Adjust Cache Size}

The first experiment fix hit rate to 100\%,
and adjust the size of cache (the number of key-value pairs).

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{adjust_cache_size.png}
  \caption{adjust cache size}
\end{figure}

In Fig. 5, we can see that time cost by doubly-linked list
is proportional to the cache size. It's because that
the main cost of doubly-linked list is on replication.
How big is the cache, how much is the amount to be copied each time the block is updated

The growth curve of the red-black tree and the sequence
tree is rather gentle ($O(\log n)$).
Noting that the line graph of the order tree,
compared to the smooth growth of the red-black tree,
is somewhat oscillating,
Because the number of leaves of the
order tree is $1 + \lceil \log_2 n \rceil$,
its number of leaves is more discrete,
When the cache size reaches the power of $2^k$,
the number of leaves doubles, which will affect
the performance and cause oscillating.

\subsubsection{Adjust hit rate}

In this experiment, we fix cache size to 30000, and adjust hit rate.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{adjust_hit_rate.png}
  \caption{adjust hit rate}
\end{figure}

In Fig 6, we can see that the hit rate has no effect
on the doubly linked list, because its main consumption
comes from replication, the only thing to do
after the cache hit is to move a few pointer,
it doesn't take much time.
The time consumption of red-black trees and order
trees will increase with the increase of hit rate.
Because their main time-consuming comes from path copying,
the more cache hits, the more branches need
to be copied and created.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{adjust_put_rate.png}
  \caption{adjust put rate}
\end{figure}

Set the cache size to 30000, the hit rate to 1.0,
and adjust the proportion of put in the get/put instructions.
It can be seen from Figure 7 that the performance
is basically not affected.

\subsection{Miss Penalty}

When verifying a transaction whose related account information
is not in the cache of the node (cache miss),
This transaction must be accompanied by a proof
for verification. Therefore, There are two penalties when cache miss:
(1) It cost network I/O to receive the proof, which is directly related
to the size of the proofs.
(2) The CPU execution time consumed by the proof verification.

From Fig 7 we can know that, when cache size is 30000,
put rate is 100\%, hit rate is 1.0, order tree implementation
can process 1000 blocks in 1.241 seconds, that means 
the average time to process a block is 1.241 milliseconds.
This number will be smaller when the cache size is smaller.

We chose Merkle Patricia tree verification cost to compare
with the order tree implementation,
We choose \href{https://docs.rs/trie-db/0.20.1/trie_db/index.html}{trie-db} module,
which is the part of one of the two major
Ethereum implementations,
\href{https://www.parity.io/ethereum/}{Parity Ethereum}, to conduct experiment.

There are two factors that influence
Merkle Patricia proof's verification performance:
(1) If the number of leaves is $s$,
the size of the proof is about $O(\log s)$.
The time complexity of verifying a proof is also $O(\log s)$.
(2) The number of proof in one batch.
A Merkle proof is a branch of the Merkle tree.
When a node is shared by multiple branches,
there is no need to repeat calculations.
So the time to verify $k$ proofs at a time will be
shorter than $k$ times the time to verify a proof.

By the information of \href{https://www.etherchain.org/charts/totalAccounts}{etherchain.org},
the number of Ethereum accounts today has exceeded 80 million,
So we first randomly insert 80 million pieces
of data into the Merkle Patricia
tree (that is, the number of leaves is 80 million),
And based on the assumption of 500 transactions in
one block, we batch verify 500 proofs at a time,
The measured time is 5.536 milliseconds, which is
obviously more time-consuming than direct access to cache.

In the aspect of I/O overhead, the proof size of a
block is about 900 KB, and 1000 blocks is almost 900 MB.
If we use the common home network today,
the time required to download these additional
proof is more time-consuming than verifying the proofs.

\subsection{Experiment Conclusion}

The Experiments verify that order tree and red-black tree
have lower time complexity. When the cache size increases
to a certain extent, they significantly beat ever-copy
doubly linked list in performance. Compared with
red-black tree, order tree does not need to maintain
the color of the node, and to execute various rotation rules,
There is a little advantage in execution speed.

At the same time, we also experimented and measured
the proof size and verification speed of the Merkle
Patricia tree. Understand that under normal circumstances,
reading the cache directly is faster than downloading
and verifying the proof. Based on these data,
it can be deduced that if Merkle Patricia tree
is used as vector commitment, if the shallow state
blockchain adopts an appropriate cache size, it
can bring speed improvement under the LRU strategy.
